Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/segmented_invariant_confluence.tex
Moved some stuff to tech report.
The paper is a bit long. I'm starting to move some content out of the
paper and into an unoffical technical report. I introduced a techreport
environment to selectively remove or include these parts.

\subsection{Discussion and Limitations}
There are a couple of things worth noting about segmented
\invariantconfluence{}, its system model, and its decision procedure.
%
First, \invariantconfluence{} is a very coarse-grained property. If an object
is \invariantconfluent{}, then we can replicate it with no coordination. If it
is not \invariantconfluent{}, then we have no guarantees. There's no
in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
more fine-grained property that can be applied to applications with varying
degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
complex applications that require a large number of segments and to simple
applications with a smaller number of segments, whereas \invariantconfluence{}
only provides guarantees to applications that can be segmented into a single
segment.

% Second, segmented \invariantconfluence{} naturally subsumes a distributed
% locking approach to replicating non-\invariantconfluent{} objects.  This
% approach first recognizes which transactions cannot be safely executed
% concurrently and then requires them to acquire a distributed lock before
% executing~\cite{balegas2015putting, gotsman2016cause}. For example, in a
% banking application with the invariant that all balances remain non-negative,
% concurrent deposits are permitted, but concurrent withdrawals can lead to
% invariant violations. Thus, we require that withdrawals acquire a distributed
% lock before executing. This example is exactly the same as
% \exampleref{CounreachableExample} which we handled by simply removing
% withdrawal transactions from our segmentation's set of transactions.

% Second, we can integrate a couple of optimizations into our system model to
% further reduce the amount of coordination it requires. To begin, if a server with
% state $s_i$ and active segment $(I_i, T_i)$ receives a transaction $t \in I_i$
% to execute, and $t(s_i)$ violates the active invariant but not the global
% invariant, instead of initiating a round of global coordination, $p_i$ can
% simply buffer $t$ for re-execution at a later time. While this increases the
% latency required to execute $t$, it's possible that after other transactions
% are executed, re-executing $t$ may lead to a state that either satisfies the
% active invariant or violates the global invariant. In either case, a round of
% global coordination is avoided. Similarly, servers can buffer transactions that
% require global coordination, executing an entire batch of these transactions
% during a single round of global coordination.

% Second, we can integrate a couple of optimizations into our system model to
% further reduce the amount of coordination it requires. For example, servers can
% buffer transactions that require global coordination, executing an entire batch
% of these transactions during a single round of global coordination.
%
% Third, a segmented \invariantconfluence{} decision procedure can also leverage
% \thmref{LatticeProperty} in addition to
% \algoref{ArbitraryStartInteractiveDecisionProcedure}. If an object $O$ meets
% criteria (1) - (3), then it is \sticonfluent{s}{T}{I} for every state $s \in
% I$.

@@

>>>>

\subsection{Discussion and Limitations}
There are a few things worth noting about segmented \invariantconfluence{}, its
system model, and its decision procedure.
%
First, \invariantconfluence{} is a very coarse-grained property. If an object
is \invariantconfluent{}, then we can replicate it with no coordination. If it
is not \invariantconfluent{}, then we have no guarantees. There's no
in-between.  Segmented \invariantconfluence{}, on the other hand, is a much
more fine-grained property that can be applied to applications with varying
degrees of complexity. Segmented \invariantconfluence{} provides guarantees to
complex applications that require a large number of segments and to simple
applications with a smaller number of segments, whereas \invariantconfluence{}
only provides guarantees to applications that can be segmented into a single
segment.

@@

\begin{techreport}

  Third, segmented \invariantconfluence{} naturally subsumes a distributed
  locking approach to replicating non-\invariantconfluent{} objects. This
  approach first recognizes which transactions cannot be safely executed
  concurrently and then requires them to acquire a distributed lock before
  executing~\cite{balegas2015putting, gotsman2016cause}. For example, in a
  banking application with the invariant that all balances remain non-negative,
  concurrent deposits are permitted, but concurrent withdrawals can lead to
  invariant violations. Thus, we require that withdrawals acquire a distributed
  lock before executing. This example is exactly the same as
  \exampleref{CounreachableExample} which we handled by simply removing
  withdrawal transactions from our segmentation's set of transactions.

  Fourth, we can integrate a couple of optimizations into our system model to
  further reduce the amount of coordination it requires. To begin, if a server
  with state $s_i$ and active segment $(I_i, T_i)$ receives a transaction $t
  \in I_i$ to execute, and $t(s_i)$ violates the active invariant but not the
  global invariant, instead of initiating a round of global coordination, $p_i$
  can simply buffer $t$ for re-execution at a later time. While this increases
  the latency required to execute $t$, it's possible that after other
  transactions are executed, re-executing $t$ may lead to a state that either
  satisfies the active invariant or violates the global invariant. In either
  case, a round of global coordination is avoided. Similarly, servers can
  buffer transactions that require global coordination, executing an entire
  batch of these transactions during a single round of global coordination.

  Fifth, a segmented \invariantconfluence{} decision procedure can also
  leverage \thmref{LatticeProperty} in addition to
  \algoref{ArbitraryStartInteractiveDecisionProcedure}. If an object $O$ meets
  criteria (1) - (3), then it is \sticonfluent{s}{T}{I} for every state $s \in
  I$.
\end{techreport}
